---
title: "factor analysis parent reported behavior items 2"
author: "Jiaqing Zhang"
output: word_document
---
##import dataset
```{r, import data}
library(haven)
msb_outcome<- read_sav("~/parent behavior items/MSB_AGG.sav")
```

#1.conduct the factor analysis for the continuous variables
```{r}
#correlation matrix  
prb.con<-msb_outcome[complete.cases(msb_outcome[, 7:11]),]
prb.cor<-round(cor(prb.con[, 7:11]),3)
prb.cor

#visualize the correlation matrixvisualize the correlation matrix
library(corrplot)
    ##ordered by first principal component scores
corrplot(prb.cor, order = "FPC")
```


##2. PCA analysis to reduce a set of observed variables
  ##2.1 eigen values and eigen vectors
```{R eigen values and eigen vectors}
#eigen values and eigen vectors
eigenvalue<-round (eigen(prb.cor)$values, 2)
eigenvector<-round (eigen(prb.cor)$vectors, 2)
eigenvalue
eigenvector
```

  ##2.2 princomp and determine the number of components
```{R princomp}
pca_pri<-princomp(prb.con[, 7:11], cor=TRUE)
summary(pca_pri)
#loadings in princomp are eigenvector

#determine number of components
    ##eigen values and eigen vectors; method 1-based on eigen values (decision rule:larger than 1), we choose 2 components.
    sum(round(eigenvalue,2)>1)
    #method 2-proportion of total variance explained (account for 80%), we choose 4 components.
    cumsum(eigenvalue/sum(eigenvalue))
    ##method 3-scree plot (prior to the elbow), we choose 5 components.
    plot(pca_pri, type="l", main="scree plot")
    ##method 4-parallel test, we choose 2 components.
    library(paran)
    paran(prb.con[, 7:11], iterations = 5000, centile=0, quietly = FALSE,, status = TRUE, all=TRUE, cfa=FALSE, graph=TRUE, color=TRUE, col=c("black", "red", "blue"), lty=c(1,2,3))
  
```    
    
  ##2.3 3 components
        first component will include: 71, 73
        second component will include: 79, 80, 82
        
```{R, 2 components}    
#the results suggested 2 components
library(psych)
prin_pca<-principal(prb.con[, 7:11], nfactors=2,covar=FALSE, scores=TRUE,rotate="varimax")
   ##loadings
   prin_pca$loadings
   ##communality
   prin_pca$communality
#visualize the structure of the pc 
library(qgraph)
qgraph.pca(prb.con[, 7:11], factors=2, rotation = "varimax", layout="tree",cut=0.4, minimum=0.2, label.cex=1.5)
```
##3. Cronbach's alpha analysis for 5 items:
     raw-alpha=0.75, indicate good reliability; 
     if re-3, re-9, re-16 are dropped, we will have a higher reliability; 
     if we drop 1, 2, 4, 10, 11, 13, the reliability will remain the same. 
     
     With three components:
     first component: the total reliability is 0.77.
     second component: the total reliability is 0.77.
     third component: the total reliability is 0.21.

```{R reliability analysis}
#reliability for items within each components 
  #with two components
      #first
      rela_pri1st<-alpha(prb.con[, 7:8])
      rela_pri1st
      #second
      rela_pri2nd<-alpha(prb.con[, 9:11])
      rela_pri2nd
```